---
title: "Weight of Fish"
author: "Robert Solis"
date: "`r Sys.Date()`"  
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5

 
    
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
require(leaps)
require(car)
```

# Predicting Fish Weight
```{r}
fish <- read.csv(file = "Fish.csv")
```

```{r eval=TRUE}
 
fish <- fish %>%
mutate(across(where(is.character), as.factor))
levels(fish$Species)
Bream <- filter(fish, Species == "Bream")
Bream <- select(Bream, -Species) 
Parkki <- filter(fish, Species == "Parkki")
Parkki <- select(Parkki, -Species) 
Perch <- filter(fish, Species == "Perch")
Perch <- select(Perch, -Species) 
Pike <- filter(fish, Species == "Pike")
Pike <- select(Pike, -Species) 
Roach <- filter(fish, Species == "Roach")
Roach <- select(Roach, -Species) 
Smelt <- filter(fish, Species == "Smelt")
Smelt <- select(Smelt, -Species) 
Whitefish <- filter(fish, Species == "Whitefish")
Whitefish <- select(Whitefish, -Species) 
```

# For each of the three species of fish listed below, determine the best regression model and also the best 2 element regression model. Use the BestSubset Regression helper file.


## Perch

### Best Models
```{r}
best.model <- lm(Weight~Height+Width,data=Perch)
summary(best.model)
```
The adjusted r squared is .94 and the standard residual error is 85.17. the p value is 2.2.

### Best Two regressor model
```{r}
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Perch,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")
summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
subsets(regsubsets.out,statistic="adjr2",legend="topright",main="Adjusted R^2")
```
Length 1 and 2 model are the best models for perch, their best two regressors models are height and width




## Pike
```{r}
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Pike,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")
summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```
L1 and L3 are the best regression models
### Best Models
```{r}
Pikebest <- lm(Weight~.,data=Pike)
summary(Pikebest)
```
The r squared is .9859 and the residual error is 70.86. The p value is 8.679. This is the best model


```{r}
Piketwo <-lm(Weight~Length1+Length3, data=Pike)
summary.lm(Piketwo)
```
This model suummarizes our best two regression models. The standard residual error is 92.56. The R R-squared is  0.9693. The  p-value: 2.572. The smallest P value is the best reslut here.

### Best Two regressor model

## Roach

### Best Models
```{r}
Roachbest <- lm(Weight~.,data=Roach)
summary(Roachbest)
```
The Residual standard error is 37.58, while the R-squared is 0.8681. And the p-value is  1.02.
### Best Two regressor model
```{r}
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Roach,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")
summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
subsets(regsubsets.out,statistic="adjr2",legend="bottom",main="Adjusted R^2")
```
The best regression model is all of them. The two best regression models are L1 and L3 similar to the first example taken there both the same model.

## Final Summary Statements